### 2018-07-06 submission/manuscript.Rmd
fix typo and update sentence

***Polymerase dependent differences in taxa are more pronounced in mock versus fecal samples.***
Finding minimal differences in overall bacterial community composision, we next examined if specific taxa vary depending on polymerase and number of cycles. Further investigation of mock community samples found that OTUs taxonomically classified to *Salmonella*, *Escherichia*, *Enterococcus*, and *Staphylococcus* differed based on polymerase used [Table S6 & S7]. These specific OTUs were all members of the mock community [Table S7]. The majority of the differences between taxa were due to differences between Kappa and the other polymerases [Table S7]. When differences in OTUs based on polymerase were investigated for fecal samples, no differences could be found (P-value $\geqslant$ `r round(min(pull(fecal_otu_tests, p.value)), digits = 2)`, corrected P-value = `r round(min(pull(fecal_otu_tests, bh)), digits = 2)`). These results suggest that taxa specific differences in mock community samples do not carry over to actual fecal community samples.

>>>>

***Polymerase dependent differences in taxa are more pronounced in mock versus fecal samples.***
Finding minimal differences in overall bacterial community composition, we next examined if specific taxa vary depending on polymerase and number of cycles. Further investigation of mock community samples found that OTUs taxonomically classified to *Salmonella*, *Escherichia*, *Enterococcus*, and *Staphylococcus* differed based on polymerase used [Table S6 & S7]. These specific OTUs were all members of the mock community and the differences were most pronounced at 25 and 30 cycles [Table S7]. The majority of the differences between taxa were due to differences between Kappa and the other polymerases [Table S7]. When differences in OTUs based on polymerase were investigated for fecal samples, no differences could be found at any number of cycles (P-value $\geqslant$ `r round(min(pull(fecal_otu_tests, p.value)), digits = 2)`, corrected P-value = `r round(min(pull(fecal_otu_tests, bh)), digits = 2)`). These results suggest that taxa specific differences in mock community samples do not carry over to actual fecal community samples.

### 2018-07-06 submission/manuscript.tex
fix typo and update sentence

\textbf{\emph{Polymerase dependent differences in taxa are more
pronounced in mock versus fecal samples.}} Finding minimal differences
in overall bacterial community composision, we next examined if specific
taxa vary depending on polymerase and number of cycles. Further
investigation of mock community samples found that OTUs taxonomically
classified to \emph{Salmonella}, \emph{Escherichia},
\emph{Enterococcus}, and \emph{Staphylococcus} differed based on
polymerase used {[}Table S6 \& S7{]}. These specific OTUs were all
members of the mock community {[}Table S7{]}. The majority of the
differences between taxa were due to differences between Kappa and the
other polymerases {[}Table S7{]}. When differences in OTUs based on
polymerase were investigated for fecal samples, no differences could be
found (P-value \(\geqslant\) 0.01, corrected P-value = 1). These results
suggest that taxa specific differences in mock community samples do not
carry over to actual fecal community samples.

>>>>

\textbf{\emph{Polymerase dependent differences in taxa are more
pronounced in mock versus fecal samples.}} Finding minimal differences
in overall bacterial community composition, we next examined if specific
taxa vary depending on polymerase and number of cycles. Further
investigation of mock community samples found that OTUs taxonomically
classified to \emph{Salmonella}, \emph{Escherichia},
\emph{Enterococcus}, and \emph{Staphylococcus} differed based on
polymerase used {[}Table S6 \& S7{]}. These specific OTUs were all
members of the mock community and the differences were most pronounced
at 25 and 30 cycles {[}Table S7{]}. The majority of the differences
between taxa were due to differences between Kappa and the other
polymerases {[}Table S7{]}. When differences in OTUs based on polymerase
were investigated for fecal samples, no differences could be found at
any number of cycles (P-value \(\geqslant\) 0.01, corrected P-value =
1). These results suggest that taxa specific differences in mock
community samples do not carry over to actual fecal community samples.
